---
title: "Unconscious EC RRR"
subtitle: "The influence of prior beliefs on conclusions"
author: "Ian Hussey^[Ghent University. Email: ian.hussey@ugent.be]"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    number_sections: no
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, 
                      message = FALSE, 
                      warning = FALSE)

# options
options(knitr.table.format = "html") # necessary configuration of tables

# disable scientific notation
options(scipen = 999) 

```

# Data, dependencies & functions

```{r}

# Dependencies ----

library(MASS)
library(tidyverse)
library(knitr)
library(kableExtra)
library(MAd)
library(weightr)
library(brms)
library(parallel)
library(timesavers)
library(bayestestR)
library(patchwork)
library(tidybayes)
library(sjPlot)
library(broom)
library(future)
library(furrr)

# Data ----

# data from pubished studies 

## Miguel's code for effect aggregation, used for consistency:

# read the file:
data_published <- read.csv("../../unconscious-ec-RRR/meta analysis of previous studies/data/meta-analysis_exclude_awere.csv")

data_identifiers <- data_published %>%
  mutate(identifier = paste(paper, compid)) %>%
  distinct(identifier)

data_published_aggregated <- data_published %>%
  agg(id = compid, 
      es = g, 
      var = var.g, 
      cor = 0.5,
      method = "BHHR",
      data = .) %>%
  bind_cols(data_identifiers) %>%
  mutate(study = identifier,
         hedges_g = es,
         hedges_g_se = sqrt(var)) %>%
  dplyr::select(study, hedges_g, hedges_g_se)


# data from rrr

data_rrr_participant_level <- read.csv("../../unconscious-ec-RRR/data/processed/data_processed.csv") %>%
  rename(DV = sum_score_evaluation_CSpos_preferred) %>%
  mutate(exclude_all_four_combined = ifelse(exclude_aware_olsen_and_fazio +
                                              exclude_aware_olsen_and_fazio_modified +
                                              exclude_awareness_baranan_dehouwer_nosek +
                                              exclude_awareness_baranan_dehouwer_nosek_modified > 0, 1, 0)) %>%
  filter(exclude_surveillance == FALSE & 
           simulated_data == FALSE & 
           exclude_all_four_combined == FALSE) %>%
  mutate(data_collection_site = dplyr::recode(data_collection_site,
                                              "Balas and Sarzynnska" = "Balas",
                                              "Corneille and Mierop" = "Mierop",
                                              "Gast Richter and Benedict" = "Gast",
                                              "Gawronski" = "Gawronski",
                                              "Hutter" = "Hütter",
                                              "Kurdi and Ferguson" = "Kurdi",
                                              "Moran Hussey and Hughes" = "Moran",
                                              "Olsen and Fritzlen" = "Olson",
                                              "Smith and Douglas" = "Douglas",
                                              "Stahl Bading Aust Heycke and Thomasius" = "Stahl",
                                              "Unkelbach and Hogden" = "Unkelbach",
                                              "Vadillo" = "Vadillo")) %>%
  dplyr::select(data_collection_site,
                DV,
                condition) 

data_rrr_site_level <- data_rrr_participant_level %>%
  group_by(data_collection_site) %>%
  dplyr::summarize(preference_mean = mean(DV),
                   preference_sd = sd(DV),
                   preference_n = n()) %>%
  # must have greater than N=2 per site to calculate SD etc
  filter(preference_n > 2) %>%
  # calculate h and its SE
  dplyr::mutate(preference_cohens_dz = preference_mean/preference_sd,
                cohens_dz_V = ((preference_n*2)/(preference_n^2)) +
                  ((preference_cohens_dz^2) / (preference_n*4)),
                J = 1 - (3/(4*(preference_n-1)-1)),
                hedges_g = preference_cohens_dz * J,
                hedges_g_V = J^2 * cohens_dz_V,
                hedges_g_se = sqrt(hedges_g_V)) %>%
  ungroup() %>%
  dplyr::select(data_collection_site, hedges_g, hedges_g_se)

```

# Creating priors using posteriors from published literature

## Meta analyis of published literature

```{r}

fit_published <- 
  brm(formula       = hedges_g | se(hedges_g_se) ~ 0 + Intercept + (1 | study),
      prior         = c(prior(normal(0, 1), class = b),
                        prior(cauchy(0, 1), class = sd)),
      family        = gaussian(),
      data          = data_published_aggregated, 
      iter          = 6000,
      control       = list(adapt_delta = 0.95),
      cores         = parallel::detectCores(), 
      chains        = 4,
      save_all_pars = TRUE,
      sample_prior  = TRUE,
      file          = "models/fit_published")

tab_model(fit_published)

```

```{r}

posterior_published_literature <- 
  fit_published %>%
  posterior_samples() %>%
  dplyr::select(b_Intercept, sd_study__Intercept)

ggplot(posterior_published_literature, aes(sd_study__Intercept)) +
  geom_density()

ggplot(posterior_published_literature, aes(b_Intercept)) +
  geom_density()

fitdistr(posterior_published_literature$b_Intercept,"normal")

# sigma will use cauchy distribution with scaling factor = mean of posterior sigma. i.e., 50% chance that it will fall within 0 < scaling factor
mean(posterior_published_literature$sd_study__Intercept)

```

## Meta analysis with publicaiton bias correction method

Posterior of Egger method bias corrected meta Miguel reported as prior for RRR meta, i.e., entering SE as a covariate.

```{r}

fit_published_egger <- 
  brm(formula       = hedges_g | se(hedges_g_se) ~ 0 + Intercept + hedges_g_se + (1 | study),
      prior         = c(prior(normal(0, 1), class = b),
                        prior(cauchy(0, 1), class = sd)),
      family        = gaussian(),
      data          = data_published_aggregated, 
      iter          = 6000,
      control       = list(adapt_delta = 0.95),
      cores         = parallel::detectCores(), 
      chains        = 4,
      save_all_pars = TRUE,
      sample_prior  = TRUE,
      file          = "models/fit_published_egger")

tab_model(fit_published_egger)

```

```{r}

posterior_published_literature_egger <- 
  fit_published_egger %>%
  posterior_samples() %>%
  dplyr::select(b_Intercept, sd_study__Intercept)

ggplot(posterior_published_literature_egger, aes(sd_study__Intercept)) +
  geom_density()

ggplot(posterior_published_literature_egger, aes(b_Intercept)) +
  geom_density()

fitdistr(posterior_published_literature_egger$b_Intercept,"normal")

# sigma will use cauchy distribution with scaling factor = mean of posterior sigma. i.e., 50% chance that it will fall within 0 < scaling factor
mean(posterior_published_literature_egger$sd_study__Intercept)

```

## Priors

NB all use Sigma = cauchy(location = 0.00, scaling = 0.50) for the sd of the random effect for site.

```{r}

read.csv("priors.csv") %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

p_priors <-
  ggplot(data = data.frame(x = c(-3, 3)), aes(x)) +
  stat_function(fun = dnorm, n = 1001, 
                args = list(mean = 0.2, sd = 0.05), 
                size = 0.6,
                aes(color = "1. Well-estimated real effect", 
                    linetype = "1. Well-estimated real effect")) + 
  stat_function(fun = dnorm, n = 1001, 
                args = list(mean = 0.2, sd = 0.25), 
                size = 0.6,
                aes(color = "2. Poorly-estimated real effect", 
                    linetype = "2. Poorly-estimated real effect")) + 
  stat_function(fun = dnorm, n = 1001, 
                args = list(mean = 0.0, sd = 0.05), 
                size = 0.6,
                aes(color = "3. Well-estimated null effect", 
                    linetype = "3. Well-estimated null effect")) + 
  stat_function(fun = dnorm, n = 1001, 
                args = list(mean = 0.0, sd = 0.25), 
                size = 0.6,
                aes(color = "4. Poorly-estimated null effect", 
                    linetype = "4. Poorly-estimated null effect")) + 
  scale_colour_brewer(type = "qual", palette = 6) +
  ylab("Probability density") +
  xlab(bquote("Prior effect size" ~ delta)) +
  coord_cartesian(xlim = c(-0.6, 0.6)) + 
  labs(color = "Prior", linetype = "Prior") +
  theme_minimal() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) 

p_priors

```

# Power analyses via simulation studies

Based on Solomon Kurz's [example](https://solomonkurz.netlify.com/post/bayesian-power-analysis-part-i/) of a fixed effects only model.

Changes:

- Parallelisation speeds up runtime - cuts time by more than 75% on my pc. Moved from purrr::map to furrr::future_map
- Simulates data with a multilevel structure with known sigma.
- Simulates impact of weak vs strong priors located on null vs true effect
- Simulates not only power to detect true effect but also probability of detecting effect inside ROPE, and probability of HDI containing true value. 

## Setup

```{r}

# function to simulate data
simulate_data <- function(effect_size, k_sites, n_per_site, between_site_variation) {
  
  data_sim <- 
    # simulate participant level data
    data.frame(sim_participant_id = 1:(n_per_site*k_sites), 
               DV = rnorm((n_per_site*k_sites), mean = effect_size, sd = 1)) %>%
    mutate(data_collection_site = paste0("site_", ((sim_participant_id-1) %/% n_per_site) + 1)) %>%
    # create site level summary scores
    group_by(data_collection_site) %>%
    dplyr::summarize(preference_mean = mean(DV),
                     preference_sd = sd(DV),
                     preference_n = n()) %>%
    # calculate h and its SE
    dplyr::mutate(preference_cohens_dz = preference_mean/preference_sd,
                  cohens_dz_V = ((preference_n*2)/(preference_n^2)) +
                    ((preference_cohens_dz^2) / (preference_n*4)),
                  J = 1 - (3/(4*(preference_n-1)-1)),
                  hedges_g = preference_cohens_dz * J,
                  hedges_g_V = J^2 * cohens_dz_V,
                  hedges_g_se = sqrt(hedges_g_V)) %>%
    ungroup() %>%
    dplyr::select(data_collection_site, hedges_g, hedges_g_se) %>%
    # stimulate between site variation
    rowwise() %>%
    mutate(site_variation = rnorm(n = 1, mean = 0, sd = between_site_variation),
           hedges_g = hedges_g + site_variation) %>%
    ungroup()
  
  return(data_sim)
  
}

# function to upated models with newly simulated data
simulation_iteration <- function(seed, data, fitted_model, effect_size, ...) {

  # set seed
  set.seed(seed)
  
  # simulate data
  data_sim <- simulate_data(effect_size            = effect_size,
                            k_sites                = k_sites,
                            n_per_site             = n_per_site,
                            between_site_variation = between_site_variation)
  
  # fit model
  fit <- 
    update(fitted_model,
           newdata = data_sim, 
           seed    = seed) %>% 
    broom::tidy(prob = .95) %>% 
    filter(term == "b_Intercept")
  
  return(fit)
  
}

# parameters
k_sites                <- pull(count(data_rrr_site_level)) 
n_per_site             <- pull(round(count(data_rrr_participant_level)/k_sites, 0))
true_effect_size       <- 0.17  # started with 0.16, from frequentist power analysis
rope_half_width        <- true_effect_size
between_site_variation <- 0.10  # rounded down from meta of existing literature, given RRR's stardardized methods its likely to be lower
n_sim                  <- 300


# fit archetypal model fits, which will be updated with new data in each sim
fit_good_real_sim_archetype <- 
  brm(formula       = hedges_g | se(hedges_g_se) ~ 0 + Intercept + (1 | data_collection_site),
      prior         = c(prior(normal(0.20, 0.05), class = b),
                        prior(cauchy(0.00, 0.25), class = sd)),
      family        = gaussian(),
      data          = simulate_data(effect_size            = true_effect_size,
                                    k_sites                = k_sites,
                                    n_per_site             = n_per_site,
                                    between_site_variation = between_site_variation), 
      seed          = 1,
      iter          = 6000,
      #control       = list(adapt_delta = 0.95),
      cores         = parallel::detectCores(), 
      chains        = 4,
      save_all_pars = TRUE,
      sample_prior  = TRUE,
      file          = "models/fit_good_real_sim_archetype")

fit_poor_real_sim_archetype <- 
  brm(formula       = hedges_g | se(hedges_g_se) ~ 0 + Intercept + (1 | data_collection_site),
      prior         = c(prior(normal(0.20, 0.25), class = b),
                        prior(cauchy(0.00, 0.25), class = sd)),
      family        = gaussian(),
      data          = simulate_data(effect_size            = true_effect_size,
                                    k_sites                = k_sites,
                                    n_per_site             = n_per_site,
                                    between_site_variation = between_site_variation), 
      seed          = 1,
      iter          = 6000,
      #control       = list(adapt_delta = 0.95),
      cores         = parallel::detectCores(), 
      chains        = 4,
      save_all_pars = TRUE,
      sample_prior  = TRUE,
      file          = "models/fit_poor_real_sim_archetype")

fit_poor_null_sim_archetype <- 
  brm(formula       = hedges_g | se(hedges_g_se) ~ 0 + Intercept + (1 | data_collection_site),
      prior         = c(prior(normal(0.00, 0.25), class = b),
                        prior(cauchy(0.00, 0.25), class = sd)),
      family        = gaussian(),
      data          = simulate_data(effect_size            = true_effect_size,
                                    k_sites                = k_sites,
                                    n_per_site             = n_per_site,
                                    between_site_variation = between_site_variation), 
      seed          = 1,
      iter          = 6000,
      #control       = list(adapt_delta = 0.95),
      cores         = parallel::detectCores(), 
      chains        = 4,
      save_all_pars = TRUE,
      sample_prior  = TRUE,
      file          = "models/fit_poor_null_sim_archetype")

fit_good_null_sim_archetype <- 
  brm(formula       = hedges_g | se(hedges_g_se) ~ 0 + Intercept + (1 | data_collection_site),
      prior         = c(prior(normal(0.00, 0.05), class = b),
                        prior(cauchy(0.00, 0.25), class = sd)),
      family        = gaussian(),
      data          = simulate_data(effect_size            = true_effect_size,
                                    k_sites                = k_sites,
                                    n_per_site             = n_per_site,
                                    between_site_variation = between_site_variation), 
      seed          = 1,
      iter          = 6000,
      #control       = list(adapt_delta = 0.95),
      cores         = parallel::detectCores(), 
      chains        = 4,
      save_all_pars = TRUE,
      sample_prior  = TRUE,
      file          = "models/fit_good_null_sim_archetype")

```

## Run  

```{r message=FALSE, warning=FALSE}

if(file.exists("models/simulations.RData")){
  
  load("models/simulations.RData")
  
} else {
  
  # run simulation
  time_start <- Sys.time()
  
  # run furrr:::future_map in parallel
  plan(multiprocess)
  
  ## simulations for detecting a true effect
  simulation_good_real <-
    tibble(seed = 1:n_sim) %>% 
    mutate(tidy = future_map(seed, simulation_iteration, 
                             .progress              = TRUE,
                             effect_size            = true_effect_size,
                             fitted_model           = fit_good_real_sim_archetype,
                             k_sites                = k_sites,
                             n_per_site             = n_per_site,
                             between_site_variation = between_site_variation)) %>% 
    unnest(tidy) %>%
    mutate(true_effect = true_effect_size,
           prior = "Well-estimated real effect")
  
  simulation_poor_real <-
    tibble(seed = 1:n_sim) %>% 
    mutate(tidy = future_map(seed, simulation_iteration, 
                             .progress              = TRUE,
                             effect_size            = true_effect_size,
                             fitted_model           = fit_poor_real_sim_archetype,
                             k_sites                = k_sites,
                             n_per_site             = n_per_site,
                             between_site_variation = between_site_variation)) %>% 
    unnest(tidy) %>%
    mutate(true_effect = true_effect_size,
           prior = "Poorly-estimated real effect")
  
  simulation_poor_null <-
    tibble(seed = 1:n_sim) %>% 
    mutate(tidy = future_map(seed, simulation_iteration, 
                             .progress              = TRUE,
                             effect_size            = true_effect_size,
                             fitted_model           = fit_poor_null_sim_archetype,
                             k_sites                = k_sites,
                             n_per_site             = n_per_site,
                             between_site_variation = between_site_variation)) %>% 
    unnest(tidy) %>%
    mutate(true_effect = true_effect_size,
           prior = "Poorly-estimated null effect")
  
  simulation_good_null <-
    tibble(seed = 1:n_sim) %>% 
    mutate(true_effect = true_effect_size,
           tidy = future_map(seed, simulation_iteration, 
                             .progress              = TRUE,
                             effect_size            = true_effect_size,
                             fitted_model           = fit_good_null_sim_archetype,
                             k_sites                = k_sites,
                             n_per_site             = n_per_site,
                             between_site_variation = between_site_variation)) %>% 
    unnest(tidy) %>%
    mutate(true_effect = true_effect_size,
           prior = "Well-estimated null effect")
  
  ## simulations for detecting a null effect
  simulation_truenull_good_real <-
    tibble(seed = 1:n_sim) %>% 
    mutate(tidy = future_map(seed, simulation_iteration, 
                             .progress              = TRUE,
                             effect_size            = 0,
                             fitted_model           = fit_good_real_sim_archetype,
                             k_sites                = k_sites,
                             n_per_site             = n_per_site,
                             between_site_variation = between_site_variation)) %>% 
    unnest(tidy) %>%
    mutate(true_effect = 0,
           prior = "Well-estimated real effect")
  
  simulation_truenull_poor_real <-
    tibble(seed = 1:n_sim) %>% 
    mutate(tidy = future_map(seed, simulation_iteration, 
                             .progress              = TRUE,
                             effect_size            = 0,
                             fitted_model           = fit_poor_real_sim_archetype,
                             k_sites                = k_sites,
                             n_per_site             = n_per_site,
                             between_site_variation = between_site_variation)) %>% 
    unnest(tidy) %>%
    mutate(true_effect = 0,
           prior = "Poorly-estimated real effect")
  
  simulation_truenull_poor_null <-
    tibble(seed = 1:n_sim) %>% 
    mutate(tidy = future_map(seed, simulation_iteration, 
                             .progress              = TRUE,
                             effect_size            = 0,
                             fitted_model           = fit_poor_null_sim_archetype,
                             k_sites                = k_sites,
                             n_per_site             = n_per_site,
                             between_site_variation = between_site_variation)) %>% 
    unnest(tidy) %>%
    mutate(true_effect = 0,
           prior = "Poorly-estimated null effect")
  
  simulation_truenull_good_null <-
    tibble(seed = 1:n_sim) %>% 
    mutate(true_effect = true_effect_size,
           tidy = future_map(seed, simulation_iteration, 
                             .progress              = TRUE,
                             effect_size            = 0,
                             fitted_model           = fit_good_null_sim_archetype,
                             k_sites                = k_sites,
                             n_per_site             = n_per_site,
                             between_site_variation = between_site_variation)) %>% 
    unnest(tidy) %>%
    mutate(true_effect = 0,
           prior = "Well-estimated null effect")
  
  time_end <- Sys.time()
  
  simulations <- list(results = bind_rows(simulation_good_real,
                                          simulation_poor_real,
                                          simulation_poor_null,
                                          simulation_good_null,
                                          simulation_truenull_good_real,
                                          simulation_truenull_poor_real,
                                          simulation_truenull_poor_null,
                                          simulation_truenull_good_null),
                      time = time_end - time_start)
  
  save(simulations, file = "models/simulations.RData")
  
}

```

## Summarize sims

```{r fig.height=9, fig.width=7}

# simulation time
simulations$time

# plot
simulations$results %>%
  mutate(seed = fct_reorder(as.factor(seed), estimate),
         true_effect_string = paste("True effect =", true_effect),
         prior_string = paste("Prior:", prior)) %>%
  group_by(true_effect_string, prior_string) %>%
  mutate(id = row_number()) %>%
  ungroup() %>%
  arrange(estimate) %>%
  group_by(true_effect_string, prior_string) %>%
  mutate(id_order = row_number()) %>%
  ggplot(aes(x = id_order, y = estimate, ymin = lower, ymax = upper)) +
  facet_wrap(~ true_effect_string + prior_string, ncol = 2) +
  annotate("rect",
           xmin  = -Inf,
           xmax  = +Inf,
           ymin  = rope_half_width*-1,
           ymax  = rope_half_width,
           alpha = +0.2) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  geom_hline(aes(yintercept = true_effect), linetype = "dashed", color = "darkgreen") +
  geom_pointrange(fatten = 0.5, alpha = 0.7) +
  labs(x = "Simulation iterations",
       y = bquote("Posterior effect size" ~ delta)) +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  theme_minimal()

simulations$results %>% 
  filter(true_effect == true_effect_size & prior == "Poorly-estimated null effect") %>%
  mutate(seed = fct_reorder(as.factor(seed), estimate),
         true_effect_string = paste("True effect =", true_effect),
         prior_string = paste("Prior:", prior)) %>%
  group_by(true_effect_string, prior_string) %>%
  mutate(id = row_number()) %>%
  ungroup() %>%
  arrange(estimate) %>%
  group_by(true_effect_string, prior_string) %>%
  mutate(id_order = row_number()) %>%
  ggplot(aes(x = id_order, y = estimate, ymin = lower, ymax = upper)) +
  annotate("rect",
           xmin  = -Inf, 
           xmax  = +Inf, 
           ymin  = rope_half_width*-1,
           ymax  = rope_half_width,
           alpha = +0.2) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "black") +
  geom_hline(aes(yintercept = true_effect), linetype = "dashed", color = "darkgreen") +
  geom_pointrange(fatten = 0.5, alpha = 0.7) +
  labs(x = "Simulation iterations",
       y = bquote("Posterior effect size" ~ delta)) +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) +
  theme_minimal()

# table
simulations$results %>% 
  mutate(null_test = ifelse(lower > 0, 1, 0),
         hdi_estimation = ifelse(lower < true_effect & upper > true_effect, 1, 0),
         rope_test = ifelse(lower > (rope_half_width*-1) & upper < rope_half_width, 1, 0)) %>% 
  group_by(true_effect, prior) %>%
  summarise(mean_estimate   = round(mean(estimate), 2),
            sd_estimate     = round(sd(estimate), 2),
            power_null_test = mean(null_test),
            power_rope_test = mean(rope_test),
            power_esimation = mean(hdi_estimation)) %>%
  mutate(prior = fct_relevel(prior,
                             "Well-estimated real effect",
                             "Poorly-estimated real effect",
                             "Poorly-estimated null effect",
                             "Well-estimated null effect")) %>%
  arrange(desc(true_effect), prior) %>%
  round_df(3) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

simulations$results %>%
  filter(prior == "Poorly-estimated null effect") %>%
  mutate(null_test = ifelse(lower > 0, 1, 0),
         hdi_estimation = ifelse(lower < true_effect & upper > true_effect, 1, 0),
         rope_test = ifelse(lower > (rope_half_width*-1) & upper < rope_half_width, 1, 0)) %>%
  group_by(true_effect) %>%
  summarise(mean_estimate   = round(mean(estimate), 2),
            sd_estimate     = round(sd(estimate), 2),
            power_null_test = mean(null_test),
            power_rope_test = mean(rope_test),
            power_esimation = mean(hdi_estimation)) %>%
  arrange(desc(true_effect)) %>%
  round_df(3) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```

# Analyses of RRR data

Using compound exclusion criterion

## Fit

```{r}

### Well-estimated real effect
fit_good_real <- 
  brm(formula       = hedges_g | se(hedges_g_se) ~ 0 + Intercept + (1 | data_collection_site),
      prior         = c(prior(normal(0.20, 0.05), class = b),
                        prior(cauchy(0.00, 0.50), class = sd)), 
      family        = gaussian(),
      data          = data_rrr_site_level,
      iter          = 6000,
      control       = list(adapt_delta = 0.95),
      cores         = parallel::detectCores(), 
      chains        = 4,
      save_all_pars = TRUE,
      sample_prior  = TRUE,
      file          = "models/fit_good_real")

#summary(fit_good_real)


### Poorly-estimated real effect
fit_poor_real <- 
  brm(formula       = hedges_g | se(hedges_g_se) ~ 0 + Intercept + (1 | data_collection_site),
      prior         = c(prior(normal(0.20, 0.25), class = b),
                        prior(cauchy(0.00, 0.25), class = sd)),
      family        = gaussian(),
      data          = data_rrr_site_level, 
      iter          = 6000,
      control       = list(adapt_delta = 0.95),
      cores         = parallel::detectCores(), 
      chains        = 4,
      save_all_pars = TRUE,
      sample_prior  = TRUE,
      file          = "models/fit_poor_real")

#summary(fit_poor_real)


### Poorly-estimated null effect
fit_poor_null <- 
  brm(formula       = hedges_g | se(hedges_g_se) ~ 0 + Intercept + (1 | data_collection_site),
      prior         = c(prior(normal(0.00, 0.25), class = b),
                        prior(cauchy(0.00, 0.25), class = sd)),
      family        = gaussian(),
      data          = data_rrr_site_level, 
      iter          = 6000,
      control       = list(adapt_delta = 0.95),
      cores         = parallel::detectCores(), 
      chains        = 4,
      save_all_pars = TRUE,
      sample_prior  = TRUE,
      file          = "models/fit_poor_null")

#summary(fit_poor_null)


### Well-estimated null effect
fit_good_null <- 
  brm(formula       = hedges_g | se(hedges_g_se) ~ 0 + Intercept + (1 | data_collection_site),
      prior         = c(prior(normal(0.00, 0.05), class = b),
                        prior(cauchy(0.00, 0.50), class = sd)),
      family        = gaussian(),
      data          = data_rrr_site_level, 
      iter          = 6000,
      control       = list(adapt_delta = 0.95),
      cores         = parallel::detectCores(), 
      chains        = 4,
      save_all_pars = TRUE,
      sample_prior  = TRUE,
      file          = "models/fit_good_null")

#summary(fit_good_null)

```

## Plots 

```{r}

# solutions from https://mjskay.github.io/tidybayes/articles/tidy-brms.html

p_results <- 
  bind_rows(
    mutate(spread_draws(fit_good_real, b_Intercept), prior = "Well-estimated real effect"), 
    mutate(spread_draws(fit_poor_real, b_Intercept), prior = "Poorly-estimated real effect"),
    mutate(spread_draws(fit_poor_null, b_Intercept), prior = "Poorly-estimated null effect"),
    mutate(spread_draws(fit_good_null, b_Intercept), prior = "Well-estimated null effect")
  ) %>%
  mutate(prior = fct_relevel(prior,
                             "Well-estimated null effect",
                             "Poorly-estimated null effect",
                             "Poorly-estimated real effect",
                             "Well-estimated real effect")) %>%
  ggplot(aes(y = prior, x = b_Intercept, fill = stat(x > 0))) +
  annotate("rect",
           ymin  = -Inf, 
           ymax  = +Inf, 
           xmin  = rope_half_width*-1,
           xmax  = rope_half_width,
           alpha = +0.2) +
  geom_vline(xintercept = 0, color = "darkgrey") +
  stat_halfeyeh(.width = c(0.66, 0.95), alpha = 0.8) +
  #scale_fill_manual(values = c("gray80", "skyblue")) +
  scale_fill_viridis_d(begin = 0.4, end = 0.6) +
  xlab(bquote("Posterior effect size" ~ delta)) +
  ylab("Prior belief") +
  labs(fill = "Effect > 0") +
  theme_minimal()

p_results

```

NB 66% and 95% HDIs. ROPE was $\delta$ = `r rope_half_width*-1` to `r rope_half_width`.

## Table

```{r}

# solutions from 
# https://cran.r-project.org/web/packages/bayestestR/vignettes/credible_interval.html
# https://rdrr.io/cran/bayestestR/f/vignettes/probability_of_direction.Rmd

# Estimates

results_posterior <- 
  
  bind_rows(
    
    fit_good_real %>%
      posterior_summary(pars = "b_Intercept") %>%
      as.data.frame() %>%
      mutate(prior_certainty = "Well-estimated", 
             prior_effect = "real effect"),
    
    fit_poor_real %>%
      posterior_summary(pars = "b_Intercept") %>%
      as.data.frame() %>%
      mutate(prior_certainty = "Poorly-estimated", 
             prior_effect = "real effect"),
    
    fit_poor_null %>%
      posterior_summary(pars = "b_Intercept") %>%
      as.data.frame() %>%
      mutate(prior_certainty = "Poorly-estimated", 
             prior_effect = "null effect"),
    
    fit_good_null %>%
      posterior_summary(pars = "b_Intercept") %>%
      as.data.frame() %>%
      mutate(prior_certainty = "Well-estimated", 
             prior_effect = "null effect")
    
  ) %>%
  rownames_to_column(var = "parameter") %>%
  rename(delta = Estimate,
         error = Est.Error,
         hdi_lower = Q2.5,
         hdi_upper = Q97.5) %>%
  mutate(delta_and_hdi = paste0(bquote(.(format(round(delta, 2), nsmall = 2))), 
                                " [", 
                                bquote(.(format(round(hdi_lower, 2), nsmall = 2))),
                                ", ", 
                                bquote(.(format(round(hdi_upper, 2), nsmall = 2))),
                                "]"),
         prior = as.factor(paste(prior_certainty, prior_effect)),
         prior = fct_relevel(prior, 
                             "Well-estimated null effect", 
                             "Poorly-estimated null effect",
                             "Poorly-estimated real effect", 
                             "Well-estimated real effect")) %>%
  dplyr::select(prior, delta, hdi_lower, hdi_upper, error, delta_and_hdi) %>%
  round_df(2)


# Equivalence test via Krushke method

results_rope <- 
  bind_rows(
    mutate(bayestestR::equivalence_test(posterior_samples(fit_good_real)$b_Intercept, 
                                        ci = 0.95,
                                        range = c(rope_half_width*-1, rope_half_width),
                                        ci_method = "HDI"),
           prior = "Well-estimated real effect"),
    
    mutate(bayestestR::equivalence_test(posterior_samples(fit_poor_real)$b_Intercept, 
                                        ci = 0.95,
                                        range = c(rope_half_width*-1, rope_half_width),
                                        ci_method = "HDI"),
           prior = "Poorly-estimated real effect"),
    
    mutate(bayestestR::equivalence_test(posterior_samples(fit_poor_null)$b_Intercept, 
                                        ci = 0.95,
                                        range = c(rope_half_width*-1, rope_half_width),
                                        ci_method = "HDI"),
           prior = "Poorly-estimated null effect"),
    
    mutate(bayestestR::equivalence_test(posterior_samples(fit_good_null)$b_Intercept, 
                                        ci = 0.95,
                                        range = c(rope_half_width*-1, rope_half_width),
                                        ci_method = "HDI"),
           prior = "Well-estimated null effect")
  ) %>%
  mutate(p_in_rope = ROPE_Percentage) %>%
  dplyr::select(prior, p_in_rope) %>%
  round_df(5)

# is the posterior effect size greater than zero?
results_p_greater_zero <- 
  bind_rows(
    mutate(p_direction(fit_good_real), prior = "Well-estimated real effect"),
    mutate(p_direction(fit_poor_real), prior = "Poorly-estimated real effect"),
    mutate(p_direction(fit_poor_null), prior = "Poorly-estimated null effect"),
    mutate(p_direction(fit_good_null), prior = "Well-estimated null effect")
  ) %>%
  mutate(p_greater_zero = 1 - pd) %>%
  dplyr::select(prior, p_greater_zero) %>%
  round_df(5)

# is the posterior effect size smaller than the published literature?
results_p_less_lit <- 
  bind_rows(
    mutate(hypothesis(fit_good_real, "Intercept < 0.20", alpha = 0.25)$hypothesis, 
           prior = "Well-estimated real effect"),
    mutate(hypothesis(fit_poor_real, "Intercept < 0.20", alpha = 0.25)$hypothesis, 
           prior = "Poorly-estimated real effect"),
    mutate(hypothesis(fit_poor_null, "Intercept < 0.20", alpha = 0.25)$hypothesis, 
           prior = "Poorly-estimated null effect"),
    mutate(hypothesis(fit_good_null, "Intercept < 0.20", alpha = 0.25)$hypothesis, 
           prior = "Well-estimated null effect")
  ) %>%
  mutate(p_less_lit = 1 - Post.Prob) %>%
  select(prior, p_less_lit) %>%
  round_df(5)

# is the posterior effect size smaller than the original study we replicate?
results_p_less_orig <- 
  bind_rows(
    mutate(hypothesis(fit_good_real, "Intercept < 0.27", alpha = 0.25)$hypothesis, 
           prior = "Well-estimated real effect"),
    mutate(hypothesis(fit_poor_real, "Intercept < 0.27", alpha = 0.25)$hypothesis, 
           prior = "Poorly-estimated real effect"),
    mutate(hypothesis(fit_poor_null, "Intercept < 0.27", alpha = 0.25)$hypothesis, 
           prior = "Poorly-estimated null effect"),
    mutate(hypothesis(fit_good_null, "Intercept < 0.27", alpha = 0.25)$hypothesis, 
           prior = "Well-estimated null effect")
  ) %>%
  mutate(p_less_orig = 1 - Post.Prob) %>%
  select(prior, p_less_orig) %>%
  round_df(5)


# combined
results <- results_posterior %>%
  left_join(results_rope, by = "prior") %>%
  left_join(results_p_greater_zero, by = "prior") %>%
  left_join(results_p_less_lit, by = "prior") %>%
  left_join(results_p_less_orig, by = "prior")

# table
results %>%
  rowwise() %>%
  dplyr::select(prior, delta_and_hdi, p_greater_zero, p_in_rope, p_less_lit, p_less_orig) %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```

# Conclusions

- Conclusions reached on the basis of the data do indeed depend on prior beliefs. 
- Using 95% HDIs and/or Bayesian *p* values (i.e., 1-posterior probability of direction), the data plus a prior belief in a well-estimated true effect produced a posterior belief that was credibly different from zero. The other three priors did not give rise to a credible posterior effect, and indeed all gave rise to an effect that was 100% within the region of practical equivalence with zero. As such, differences in priors gave rise to differences not only with regard to the support for H1, but also the support for H0: three priors not only fail to find evidence for H1 but find support for H0. 
- Critically, however, the prior belief that there is a true effect (i.e., belief in the unaware EC hypothesis) was not sufficent to the posterior belief in the hypothesis: the combination of a prior belief in the effect *and* specificity in its estimation (i.e., relative confidence in the effect size range) was required for a posterior belief in the effect.  

- If you believe the results of the meta analysis of published literature, this replication study does not contain enough data to change your mind. 
- Equally, if you strongly disbelieve the effect is real, this replication does not contain enough data to change your mind.

- The analyses in Moran et al are null hypothesis tests: is the effect greater than zero. 
- Bayesian versions of this show mixed evidence that is sensitive to choice of prior.
- It is also meaningful to ask is the effect greater or smaller than the ES in the published literature. 
- Results are a more conclusive yes: Belief in the effect being non zero may be dependant on choice of prior (i.e., only a very strong prior belief in the effect being true allows posterior belief to persist), but posterior belief that the effect is substantially smaller than that found in the published literature is independant of prior. 
- As such, results give some small room to continue to believe in the effect if your prior beliefs are very strong, but they leave no doubt that effects are lower than in the published literature. 


